%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                   %
% Compile with XeLaTeX and biber    %
%                                   %
% Questions or comments:            %
%                                   %
% joshua dot mcneill at uga dot edu %
%                                   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{beamer}
  % Read in standard preamble (cosmetic stuff)
  \input{../../shared/slide_preamble.tex}

  % Packages and settings

  % Document information
  \subtitle[Bienvenue]{Bienvenue}

  %% Custom commands
  % Subsection/frame titles

\begin{document}
  % Read in the standard intro slides (title page and table of contents)
  \begin{frame}
    \titlepage
    \tiny{Office: \input{../../shared/office_location.tex}\\
          Office hours: \input{../../shared/office_hours.tex}}
  \end{frame}

  \begin{frame}{Présentations}
    \begin{center}
      Preséntez-vous à vos voisins.\\
      \gloss{Introduce yourself to your neighbors.}
    \end{center}
    \begin{itemize}
      \item[E1:] Bonjour, je m'appelle ... Et toi? Comment tu t'appelles?
      \item[E2:] Bonjour, je m'appelle ...
      \item[E1:] Moi, je suis de ... Et toi?
      \item[E2:] Moi, je suis de ...
      \item[E1:] Enchanté OR enchantée!
      \item[E2:] Enchanté OR enchantée!
    \end{itemize}
    \uncover<2->{
      \begin{center}
        Il s'appelle ... / Elle s'appelle ... \\
        Il est de ... / Elle est de ...
      \end{center}
    }
  \end{frame}

  \section{Syllabus}
  \begin{frame}
    \begin{center}
      \Huge{Syllabus}
    \end{center}
  \end{frame}

  \begin{frame}{Goals for this course}
    Basic expression and communication in French in:
    \begin{itemize}
      \item Listening
      \item Speaking
      \item Reading
      \item Writing
    \end{itemize}
  \end{frame}

  \begin{frame}{How to achieve course goals}
    Use French.
    \begin{itemize}
      \item Study and practice \alert{daily} outside of class
      \item Make every effort to practice in class
    \end{itemize}
  \end{frame}

  \begin{frame}{Materials}
    \begin{itemize}
      \item Textbook: Chez nous, 5th ed.
      \item eLC (\url{https://uga.view.usg.edu})
      \item MyFrenchLab (MFL) (\url{https://www.pearsonmylabandmastering.com})
    \end{itemize}
    \alert{Before each class}, complete the textbook reading and the MFL exercises indicated on the syllabus.
  \end{frame}

  \begin{frame}{Grading}
    \begin{center}
      \begin{tabular}{l l | l l}
        Participation      & 20\% & Quizzes           & 15\% \\
        Other Homework (5) & 10\% & Chapter Tests (2) & 20\% \\
        MyFrenchLab (MFL)  & 20\% & Final Exam        & 15\% \\
      \end{tabular}
    \end{center}
    \begin{itemize}
      \item 3 absences allowed, no questions asked
      \item 3 lowest quizzes are dropped
    \end{itemize}
  \end{frame}

  \begin{frame}{Academic honesty}
    Read, sign, and return the document Unauthorized Assistance in the French Classroom found on eLC.
    \begin{itemize}
      \item Authorized assistance: Single word translations (i.e., from a dictionary) and tutors who help \emph{you} arrive at the answer
      \item Unauthorized assistance: Automatic translation services and anyone who \emph{gives} you the answers
    \end{itemize}
  \end{frame}

  \begin{frame}{Tutoring}
    \begin{itemize}
      \item Peer tutoring at the DAE (\url{https://dae.uga.edu/services/tutoring/})
      \item Private tutoring through the department (\url{https://rom.uga.edu/tutoring})
    \end{itemize}
  \end{frame}
\end{document}
