%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                   %
% Compile with XeLaTeX and biber    %
%                                   %
% Questions or comments:            %
%                                   %
% joshua dot mcneill at uga dot edu %
%                                   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{beamer}
  % Read in standard preamble (cosmetic stuff)
  \input{../shared/slide_preamble.tex}

  % Packages and settings
  \usepackage[backend=biber, style=apa]{biblatex}
    \addbibresource{../references/References.bib}

  % Document information
  \subtitle[Syntactic Categories]{Syntactic Categories}

  %% Custom commands
  % Subsection/frame titles
  \newcommand{\suboneone}{What are they?}
  \newcommand{\subonetwo}{Some major categories}
  \newcommand{\subonethree}{Summarizing}
  \newcommand{\subonefour}{Pratice}

\begin{document}
  % Read in the standard intro slides (title page and table of contents)
  \input{../shared/slide_intro.tex}

  \section{Syntactic Categories}
    \subsection{\suboneone}
      \begin{frame}{\suboneone}
        \begin{definition}
          \input{\defs/part3/def_syntactic_category.tex}
        \end{definition}
        \begin{example}<2->
          \begin{enumerate}
            \item \lexi{the dog} \hfill (noun phrase/NP)
            \item \lexi{in January} \hfill (prepositional phrase/PP)
            \item \lexi{The dog listens to death metal in January.} \hfill (sentence/S)
          \end{enumerate}
        \end{example}
        \begin{alertblock}<3->{}
          This does not include lexical categories (e.g., \lexi{dog}, an N)
        \end{alertblock}
      \end{frame}

      \begin{frame}{\suboneone}
        \begin{alertblock}{Syntactic distribution}
          \input{\defs/part3/def_syntactic_distribution.tex}
        \end{alertblock}
        \begin{example}<2->
          \begin{enumerate}
            \item The dog listens to death metal
            \item The dog listens to jazz
            \item The dog listens to shoegaze
          \end{enumerate}
        \end{example}
        \begin{block}<2->{}
          \lexi{Death metal}, \lexi{jazz}, and \lexi{shoegaze} are all have the same distribution and are all NPs
        \end{block}
      \end{frame}

      \begin{frame}{\suboneone}
        \begin{block}{}
          Meaning is not so important
        \end{block}
        \begin{example}
          \begin{enumerate}
            \item Cooking is fun.
            \item Games are fun.
          \end{enumerate}
        \end{example}
        \begin{block}{}
          Both are NPs but \lexi{cooking} is an action and \lexi{games} a thing
        \end{block}
      \end{frame}

    \subsection{\subonetwo}
      \begin{frame}{\subonetwo}
        \begin{block}{S: Sentence}
          Made up of an NP and a VP
        \end{block}
        \begin{block}{To identify Ss}
          \begin{itemize}
            \item Sally thinks that \hrulefill
          \end{itemize}
        \end{block}
        \begin{example}<2->
          \begin{enumerate}
            \item \only<3->{*}Sally thinks that the dog.
            \item Sally thinks that the dog listens to death metal.
          \end{enumerate}
        \end{example}
      \end{frame}

      \begin{frame}[t]{\subonetwo}
        \begin{block}{NP: Noun Phrase}
          Made up of at least an N
        \end{block}
        \begin{block}{To identify NPs}
          Replace with a pronoun
        \end{block}
        \only<2-3>{
          \begin{example}
            \begin{enumerate}
              \item The dog listens to death metal.
              \item She listens to it.
              \item \only<3->{*}The she listens to death it.
            \end{enumerate}
          \end{example}
        }
        \only<4>{
          \begin{block}{Det: Determiner (a lexical category)}
            \begin{itemize}
              \item Articles: \lexi{the}, \lexi{a}, etc.
              \item Demonstratives: \lexi{this}, \lexi{those}, etc.
              \item Quantifiers: \lexi{some}, \lexi{many}, \lexi{few}, etc.
              \item Possessives: \lexi{my}, \lexi{your}, \lexi{their}, etc.
            \end{itemize}
            Can combine with Ns but not with NPs
          \end{block}
        }
        \only<5>{
          \begin{block}{NPs can be very long}
            \begin{enumerate}
              \item The tiny brown dog with a short tail from Athens listens to death metal.
              \item It listens to death metal.
            \end{enumerate}
            Contains APs and PPs
          \end{block}
        }
      \end{frame}

      \begin{frame}[t]{\subonetwo}
        \begin{block}{VP: Verb Phrase}
          Made up of at least a V
        \end{block}
        \begin{block}{To identify VPs}
          \begin{itemize}
            \item Add an NP to its left and you should have an S
            \item Replace with \lexi{does so} or \lexi{did so}
          \end{itemize}
        \end{block}
        \only<2>{
          \begin{example}
            \begin{enumerate}
              \item \rule{1cm}{0.15mm} ate gumbo. $\rightarrow$ Louis ate gumbo.
              \item Louis slept. $\rightarrow$ Louis did so.
            \end{enumerate}
          \end{example}
        }
        \only<3>{
          \begin{block}{}
            \begin{enumerate}
              \item Louis gave the tall slender man with a hat and cane the rest of his hot tasty gumbo
              \item[$\rightarrow$] Louis did so.
              \item Louis did so his gumbo.
            \end{enumerate}
          \end{block}
        }
      \end{frame}

      \begin{frame}{\subonetwo}
        \begin{block}{PP: Prepositional Phrase}
          Made up of at least a P and a NP
        \end{block}
        \begin{example}
          \begin{enumerate}
            \item \only<2->{[NP }A tall man \only<2->{[PP }with a hat\only<2->{]]}
            \item \only<3->{[VP }ate gumbo \only<3->{[PP }at the counter.\only<3->{]]}
          \end{enumerate}
        \end{example}
        \begin{block}<2->{Distribution}
          \begin{itemize}
            \item<2-> In NPs (1)
            \item<3-> In VPs (2)
          \end{itemize}
        \end{block}
      \end{frame}

      \begin{frame}{\subonetwo}
        \begin{block}{AP: Adjectival Phrase}
          Made up of at least an Adj
        \end{block}
        \begin{example}
          \begin{enumerate}
            \item \only<2->{[NP }The \only<2->{[AP }tall\only<2->{]} man\only<2->{]}
            \item \only<3->{[VP }is \only<3->{[AP }slender\only<3->{]}.\only<3->{]}
          \end{enumerate}
        \end{example}
        \begin{block}<2->{Distribution}
          \begin{itemize}
            \item<2-> In NPs (1)
            \item<3-> In VPs (2)
          \end{itemize}
        \end{block}
      \end{frame}

      \begin{frame}{\subonetwo}
        \begin{block}{Adv: Adverb (not an Adverbial Phrase)}
          Made up of at least an Adv
        \end{block}
        \begin{example}
          \begin{enumerate}
            \item \only<2->{[AP [Adv }very\only<2->{]} tall\only<2->{]}
          \end{enumerate}
        \end{example}
        \begin{block}<2->{Distribution}
          For now, only in APs
        \end{block}
      \end{frame}

    \subsection{\subonethree}
      \begin{frame}{\subonethree}
        \small
          \input{../material_syn_cats/material_syn_cats_table.tex}
      \end{frame}

    \subsection{\subonefour}
      \begin{frame}{\subonefour}
        \begin{block}{Try these}
          \textcite{dawson_language_2016}, chapter 5 exercises 17 and 19
        \end{block}
      \end{frame}

\end{document}
