%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                   %
% Compile with XeLaTeX and biber    %
%                                   %
% Questions or comments:            %
%                                   %
% joshua dot mcneill at uga dot edu %
%                                   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{beamer}
  % Read in standard preamble (cosmetic stuff)
  \input{../shared/slide_preamble.tex}

  % Packages and settings
  \usepackage[backend=biber, style=apa]{biblatex}
    \addbibresource{../references/References.bib}

  % Document information
  \subtitle[Compositional Semantics]{Compositional Semantics}

  %% Custom commands
  % Subsection/frame titles
  \newcommand{\suboneone}{Why we need it}
  \newcommand{\subonetwo}{Propositions}
  \newcommand{\subonethree}{Entailment}
  \newcommand{\subonefour}{Incompatibility}
  \newcommand{\subonefive}{Practice}
  % First example of a proposition
  \newcommand{\proptrue}{China is the most populous country in the world}

\begin{document}
  % Read in the standard intro slides (title page and table of contents)
  \input{../shared/slide_intro.tex}

  \section{Compositional Semantics}
    \subsection{\suboneone}
      \begin{frame}{\suboneone}
        \begin{block}{What do these words express together?}
          \begin{enumerate}
            \item \lexi{China}, \lexi{country}, \lexi{populous}, \lexi{world}
          \end{enumerate}
          \uncover<2->{
            What about these?
            \begin{enumerate}
              \setcounter{enumi}{1}
              \item \proptrue
            \end{enumerate}
          }
        \end{block}
        \begin{block}<2->{}
          We cannot communicate complex meanings solely through word meanings
          \begin{itemize}
            \item (2) goes beyond (1); it makes a claim
          \end{itemize}
        \end{block}
      \end{frame}

      \begin{frame}{\suboneone}
        \begin{alertblock}{Compositional semantics}
          \input{\defs/part3/def_compositional_semantics.tex}
          \begin{itemize}
            \item The basic unit of compositional semantics is the proposition
          \end{itemize}
        \end{alertblock}
      \end{frame}

    \subsection{\subonetwo}
      \begin{frame}[t]{\subonetwo}
        \begin{definition}
          \input{\defs/part3/def_proposition.tex}
          \begin{itemize}
            \item They have \alert{truth values}: \input{\defs/part3/def_truth_value.tex}
          \end{itemize}
        \end{definition}
        \only<2>{
          \begin{example}
            This proposition is true according to the world
            \begin{enumerate}
              \setcounter{enumi}{1}
              \item \proptrue
            \end{enumerate}
          \end{example}
        }
        \only<3>{
          \begin{example}
            This proposition is false according to the world
            \begin{enumerate}
              \setcounter{enumi}{2}
              \item Luxembourg is the most populous country in the world
            \end{enumerate}
          \end{example}
        }
      \end{frame}

      \begin{frame}{\subonetwo}
        \begin{block}{Truth values are based on \alert{truth conditions}}
          \input{\defs/part3/def_truth_condition.tex}
        \end{block}
        \begin{block}{What is this proposition's truth value?}
          \begin{itemize}
            \item The Queen of England is sleeping.
          \end{itemize}
          \uncover<2->{It depends on its the truth conditions.}
        \end{block}
      \end{frame}

    \subsection{\subonethree}
      \begin{frame}[t]{\subonethree}
        \begin{definition}
          \input{\defs/part3/def_entailment.tex}
        \end{definition}
        \only<-2>{
          \begin{example}
            \begin{enumerate}
              \item All dogs bark.
              \item[$\rightarrow$] Sally's dog barks.
              \item<2-> All cats bark.
              \item<2->[$\rightarrow$] Sally's cat barks.
            \end{enumerate}
            \uncover<2->{
              The first proposition becomes the truth condition for the second
            }
          \end{example}
        }
        \only<3->{
          \begin{block}{Does this work as entailment?}
            \begin{enumerate}
              \item Sally's dog barks.
              \item[$\rightarrow$] All dogs bark.
            \end{enumerate}
            \uncover<4->{
            No, this entailment relationship is asymmetric
            }
          \end{block}
        }
      \end{frame}

      \begin{frame}{\subonethree}
        \begin{alertblock}{Mutual entailment}
          \input{\defs/part3/def_mutual_entailment.tex}
        \end{alertblock}
        \begin{example}
          \begin{enumerate}
            \item Ian has a female sibling.
            \item[$\rightarrow$] Ian has a sister.
            \item Ian has a sister.
            \item[$\rightarrow$] Ian has a female sibling.
          \end{enumerate}
        \end{example}
      \end{frame}

    \subsection{\subonefour}
      \begin{frame}{\subonefour}
        \begin{definition}
          \input{\defs/part3/def_incompatibility.tex}
        \end{definition}
        \begin{example}
          \begin{enumerate}
            \item Abraham Lincoln is dead.
            \item Abraham Lincoln is alive.
          \end{enumerate}
        \end{example}
      \end{frame}

    \subsection{\subonefive}
      \begin{frame}{\subonefive}
        \begin{block}{Try these}
          \textcite{dawson_language_2016}, chapter 6 exercises 17, 18, 20, 22, and 23
        \end{block}
      \end{frame}
\end{document}
