%%%%%%%%%%%%%%%%%%%%%%%%
% Compile with XeLaTeX %
%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{article}
  % Packages and settings
  \usepackage{fontspec}
    \setmainfont{Charis SIL}
  \usepackage{hyperref}
    \hypersetup{colorlinks=true,
                allcolors=blue}
  \usepackage{longtable}
  \usepackage{caption}
    \captionsetup{labelformat=empty,
                  font=bf}
  \usepackage[backend=biber,style=apa]{biblatex}
    \addbibresource{../references/References.bib}
    \DeclareLanguageMapping{english}{english-apa}

  % Custom commands
  % Used to add a line break in a table cell
  \newcommand{\cellbreak}[2]{
    \begin{tabular}[t]{@{}l@{}}
      #1\\
      #2
    \end{tabular}}
  % Used to add some space above a row in a table
  \newcommand{\rowvspace}{\rule{0pt}{14pt}}

  % Document information
  \title{LING2100: The Study of Language\footnote{The course syllabus is a general plan for the course; deviations announced to the class by the instructor may be necessary.}}
  \author{Joshua McNeill}
  \date{Fall, 2019}

\begin{document}
  \maketitle

  \begin{center}
    \begin{tabular}{@{} l r @{}}
      E-mail: \url{joshua.mcneill@uga.edu}              & Class hours: M/W/F 1:25-2:15\\
      Office hours: \input{../shared/office_hours.tex}  & M/W/F 2:30-3:20\\
      Office: \input{../shared/office_location.tex}     & Classroom: MLC 207/MLC 147\\
      TA supervisor: Mi-Ran Kim                         & Sections: 40516/38409\\
      Super e-mail: \url{mrkim@uga.edu}
    \end{tabular}
  \end{center}

  \hrule

  \paragraph{Description}
    The \emph{scientific} study of language, emphasizing such topics as the organization of grammar, language in space and time, and the relationship between the study of language and other disciplines.

  \paragraph{Objectives}
    At the end of the course, students, having read a substantial body of material related to the scientific study of language, will be able to use linguistic terminology accurately; to discuss basic linguistic facts, theories, and methodologies; to analyze samples of written or spoken language from a variety of world languages; and to understand both language change and how language supports all learning and communication. They will be prepared to undertake more advanced and specific linguistic studies.

  \paragraph{Topics}
    The topics will consist of writings about various linguistic matters, including phonetics/phonology, morphology, syntax, lexicons, and semantics, as they relate to the general fields of sociolinguistics, historical linguistics, language acquisition, cognitive linguistics, and language variation. A number of graded tasks will be assigned, such as quizzes, tests, and various writing assignments done either in or outside of class.

  \paragraph{Course Materials}
    Everything you will need to know will be presented in class, but reading is encouraged and we \emph{will use the book during class}.
    \fullcitebib{dawson_language_2016}

  \paragraph{Grading} \mbox{}\\
    {\small
      \begin{tabular}{@{} l @{} l l l @{} l l | r l @{}}
        A   & (4.0) & 100 - 93  & C+  & (2.3) & 79.9 - 77 & Participation & 11\%\\
        A-  & (3.7) & 92.9 - 90 & C   & (2.0) & 76.9 - 73 & Homework      & 45\% (4x11\% + 1x1\%)\\
        B+  & (3.3) & 89.9 - 87 & C-  & (1.7) & 72.9 - 70 & Exams         & 44\% (4x11\%)\\
        B   & (3.0) & 86.9 - 83 & D   & (1.0) & 69.9 - 60 & \\
        B-  & (2.7) & 82.9 - 80 & F   & (0.0) & 59.9 - 0  & \\
      \end{tabular}
    }

  \paragraph{Attendance}
    Your class participation grade is mostly a function of your attendance: attend class, pay attention, ask a questions, and you will receive full credit. Three excused absences are allowed per semester (no need to explain), after which 1\% will be deducted from your final grade for each additional absence. If you find yourself in extentuating circumstances, please reach out sooner rather than later.

  \paragraph{Make-up Work}
    If you foresee that you will not be able to make it to an exam date or hand in an assignment on time, please get in touch with the instructor \emph{beforehand}. No make-ups will be allowed after the fact.

    \begin{longtable}{c l l l}
      Week  & Date (Day)  & Topic                           & Due by Scheduled Class\\
      \hline
      1     & 8/14 (W)    & Welcome \rowvspace              & \\
            & 8/16 (F)    & Phonetics                       & \cellbreak{Homework 0 due}
                                                                        {Read 2.0 and 2.1}\\
      2     & 8/19 (M)    &                                 & Read 2.2\\
            & 8/21 (W)    &                                 & Read 2.3\\
            & 8/23 (F)    &                                 & Read 2.4\\
      3     & 8/26 (M)    &                                 & Read 2.5\\
            & 8/28 (W)    &                                 & Read 2.6\\
            & 8/30 (F)    & Phonetics Review                & Homework 1 due\\
      4     & 9/2 (M)     & Labor Day/No Class              & \\
            & 9/4 (W)     & Phonetics Exam                  & \\
            & 9/6 (F)     & Phonology                       & Read 3.0 and 3.1\\
      5     & 9/9 (M)     &                                 & Read 3.2\\
            & 9/11 (W)    &                                 & Read 3.3\\
            & 9/13 (F)    &                                 & Read 3.5\\
      6     & 9/16 (M)    & Morphology                      & Read 4.0 and 4.1\\
            & 9/18 (W)    &                                 & Read 4.2\\
            & 9/20 (F)    &                                 & Read 4.3 and 4.4\\
      7     & 9/23 (M)    &                                 & Read 4.5\\
            & 9/25 (W)    & Syntax                          & Read 5.0 and 5.1\\
            & 9/27 (F)    & \cellbreak{Phonology \&}
                                      {Morphology Review}   & Homework 2 due\\
      8     & 9/30 (M)    & \cellbreak{Phonology \&}
                                      {Morphology Exam}     & \\
            & 10/2 (W)    &                                 & Read 5.2\\
            & 10/4 (F)    &                                 & Read 5.3\\
      \multicolumn{4}{c}{\textbf{Linguistics Conference at UGA (LCUGA)}\rowvspace}\\
      \multicolumn{4}{c}{\textbf{Friday \& Saturday}}\\
      9     & 10/7 (M)    & \rowvspace                      & Read 5.4\\
            & 10/9 (W)    &                                 & Read 5.5\\
            & 10/11 (F)   &                                 & \\
      10    & 10/14 (M)   &                                 & \\
            & 10/16 (W)   & Semantics                       & Read 6.0, 6.1, and 6.2\\
            & 10/18 (F)   &                                 & Read 6.3\\
      11    & 10/21 (M)   &                                 & Read 6.4\\
            & 10/23 (W)   & Pragmatics                      & Read 7.0 and 7.1\\
            & 10/25 (F)   &                                 & Read 7.2 and 7.3\\
      12    & 10/28 (M)   &                                 & Read 7.5\\
            & 10/30 (W)   & \cellbreak{Syntax, Semantics}
                                      {\& Pragmatics Review}& Homework 3 due\\
            & 11/1 (F)    & Fall Break/No Class             & \\
      13    & 11/4 (M)    & \cellbreak{Syntax, Semantics}
                                      {\& Pragmatics Exam}  & \\
            & 11/6 (W)    & Psycholinguistics               & Read 9.0, 9.1, and 9.2\\
            & 11/8 (F)    &                                 & Read 9.3\\
      14    & 11/11 (M)   &                                 & Read 9.4\\
            & 11/13 (W)   & Language Variation              & Read 10.0 and 10.1\\
            & 11/15 (F)   &                                 & Read 10.2\\
      15    & 11/18 (M)   &                                 & Read 10.3\\
            & 11/20 (W)   &                                 & Read 10.4\\
            & 11/22 (F)   & Language Change                 & Read 13.0 and 13.1\\
      16    & 11/25 (M)   &                                 & Read 13.2 and 13.3\\
            & 11/27 (W)   & Thanksgiving Break/No Class     & \\
            & 11/29 (F)   & Thanksgiving Break/No Class     & \\
      17    & 12/2 (M)    & Computational Linguistics       & Read 16.0 and 16.1\\
            & 12/4 (W)    & Final Review                    & Homework 4 due\\
            & 12/6 (F)    & \cellbreak{Final (section 38409)}
                                      {3:30-6:30}           & \\
      18    & 12/9 (M)    & \cellbreak{Final (section 40516)}
                                      {12-3}                &
    \end{longtable}

  \paragraph{University Honor Code and Academic Honesty Policy}
    As a University of Georgia student, you have agreed to abide by the University’s academic honesty policy, ``A Culture of Honesty,'' and the Student Honor Code. All academic work must meet the standards described in ``A Culture of Honesty'' found at: \url{www.uga.edu/honesty}. Lack of knowledge of the academic honesty policy is not a reasonable explanation for a violation. Questions related to course assignments and the academic honesty policy should be directed to the instructor. The link to more detailed information about academic honesty can be found at: \url{www.uga.edu/ovpi/honesty/acadhon.htm}

\end{document}
