%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                   %
% Compile with XeLaTeX and biber    %
%                                   %
% Questions or comments:            %
%                                   %
% joshua dot mcneill at uga dot edu %
%                                   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{beamer}
  % Read in standard preamble (cosmetic stuff)
  \input{../shared/slide_preamble.tex}

  % Packages and settings
  \usepackage[backend=biber, style=apa]{biblatex}
    \addbibresource{../references/References.bib}

  % Document information
  \subtitle[Syntactic Constituency]{Syntactic Constituency}

  %% Custom commands
  % Subsection/frame titles
  \newcommand{\suboneone}{What are they?}
  \newcommand{\subonetwo}{Answers to questions}
  \newcommand{\subonethree}{Clefting}
  \newcommand{\subonefour}{Pro-form substitution}
  \newcommand{\subonefive}{Interpreting the results}
  \newcommand{\subonesix}{Practice}

\begin{document}
  % Read in the standard intro slides (title page and table of contents)
  \input{../shared/slide_intro.tex}

  \section{Syntactic Constituency}
    \subsection{\suboneone}
      \begin{frame}[t]{\suboneone}
        \begin{example}
          In `The tall man ate tasty gumbo':
          \begin{enumerate}
            \item the tall man
            \item ate tasty gumbo
            \item tasty gumbo
            \item \only<2->{*}ate tasty
          \end{enumerate}
        \end{example}
        \only<1-2>{
          \begin{block}{Do these form cohesive units?}
            \begin{itemize}
              \item<2> Yes: (1-3)
              \item<2> No: (4)
            \end{itemize}
          \end{block}
        }
        \only<3>{
          \begin{alertblock}{Syntactic constituent}
            \input{\defs/part3/def_syntactic_constituent.tex}
            \begin{itemize}
              \item Identifying these helps us tease out the structure of a sentence
            \end{itemize}
          \end{alertblock}
        }
      \end{frame}

      \begin{frame}{\suboneone}
        \begin{block}{Three tests for identifying constituents}
          \begin{itemize}
            \item Answers to questions
            \item Clefting
            \item Pro-form substitution
          \end{itemize}
        \end{block}
        \begin{alertblock}{}
          This is not an exhaustive list of tests
        \end{alertblock}
      \end{frame}

    \subsection{\subonetwo}
      \begin{frame}{\subonetwo}
        \begin{block}{How it works}
          Replace some part of the sentence with a \lexi{wh-} word and form a question
          \begin{itemize}
            \item If the result is grammatical: It's a constituent
            \item If the result is ungrammatical: It's not a constituent
          \end{itemize}
        \end{block}
        \begin{example}<2->
          `The tall man ate tasty gumbo':
          \begin{itemize}
            \item \emph{Who} ate tasty gumbo?
            \item \emph{Who} the tall ate tasty gumbo?
            \item \emph{What did} the tall man do?
            \item \emph{What did} the tall man do gumbo?
          \end{itemize}
        \end{example}
      \end{frame}

    \subsection{\subonethree}
      \begin{frame}{\subonethree}
        \begin{block}{How it works}
          Move some part $X$ of the sentence $Y$ to the beginning in the format `It was $X$ who/that $Y$'
          \begin{itemize}
            \item If the result is grammatical: It's a constituent
            \item If the result is ungrammatical: It's not a constituent
          \end{itemize}
        \end{block}
        \begin{example}<2->
          `The tall man ate tasty gumbo':
          \begin{itemize}
            \item It was \emph{the tall man} who ate tasty gumbo.
            \item It was \emph{man} that the tall ate tasty gumbo.
            \item It was \emph{eat tasty gumbo} that the tall man did.
            \item It was \emph{eat tasty} that the tall man did gumbo.
          \end{itemize}
        \end{example}
      \end{frame}

    \subsection{\subonefour}
      \begin{frame}[t]{\subonefour}
        \begin{block}{How it works}
          Replace some part of the sentence with a pro-form
          \begin{itemize}
            \item If the result is grammatical: It's a constituent
            \item If the result is ungrammatical: It's not a constituent
          \end{itemize}
        \end{block}
        \only<2>{
          \begin{alertblock}{Pro-form}
            \input{\defs/part3/def_pro-form.tex}
          \end{alertblock}
          \begin{example}
            \begin{itemize}
              \item Pronouns: \emph{he}, \emph{it}, \emph{them}
              \item Pro-verbs: \emph{do}, \emph{be}, \emph{have}
            \end{itemize}
          \end{example}
        }
        \only<3>{
          \begin{example}
            `The tall man ate tasty gumbo':
            \begin{itemize}
              \item \emph{He} ate tasty gumbo.
              \item The tall \emph{he} ate tasty gumbo.
              \item The tall man \emph{did so}.
              \item The tall man \emph{did so} gumbo.
            \end{itemize}
          \end{example}
        }
      \end{frame}

    \subsection{\subonefive}
      \begin{frame}{\subonefive}
        \begin{block}{}
          \begin{itemize}
            \item Tests that are failed are not conclusive
            \item Tests that are passed are sufficient
          \end{itemize}
        \end{block}
        \begin{example}
          \begin{enumerate}
            \item *\emph{Who} the man ate tasty gumbo?
            \item<2-> \emph{Who} ate tasty gumbo?
          \end{enumerate}
          \only<1>{
            The test in (1) fails but more tests are needed to be sure
          }
          \only<2>{
            The test in (2) passes, so no more is needed
          }
        \end{example}
      \end{frame}

    \subsection{\subonesix}
      \begin{frame}{\subonesix}
        \begin{block}{Try these}
          \textcite{dawson_language_2016}, chapter 5 exercises 15 and 16
        \end{block}
      \end{frame}
\end{document}
