%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                   %
% Compile with XeLaTeX and biber    %
%                                   %
% Questions or comments:            %
%                                   %
% joshua dot mcneill at uga dot edu %
%                                   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{beamer}
  % Read in standard preamble (cosmetic stuff)
  \input{../../shared/slide_preamble.tex}

  % Packages and settings
  \usepackage[backend=biber, style=apa]{biblatex}
    \addbibresource{../references/References.bib}

  % Document information
  \subtitle[Syntax Basics]{Some Basics of Syntax}

  %% Custom commands
  % Subsection/frame titles
  \newcommand{\suboneone}{It's this}
  \newcommand{\subtwoone}{Grammaticality}
  \newcommand{\subtwotwo}{Semantics in syntax}
  \newcommand{\subtwothree}{Practice}

\begin{document}
  % Read in the standard intro slides (title page and table of contents)
  \input{../../shared/slide_intro.tex}

  \section{What is syntax?}
    \subsection{\suboneone}
      \begin{frame}{\suboneone}
        \begin{definition}
          \input{\defs/part3/def_syntax.tex}
        \end{definition}
        \begin{alertblock}<2->{}
          We're still talking about \emph{a} language: i.e., \input{\defs/part1/def_a_language.tex}
          \begin{itemize}
            \item We'll use ``English'' as shorthand for ``the set of features that happen to be shared in the languages of some group of people''
          \end{itemize}
        \end{alertblock}
        \begin{alertblock}<3->{}
          We'll be learning a phrase structure \parencite{chomsky_syntactic_2002} theory of syntax
        \end{alertblock}
      \end{frame}

  \section{Basic ideas}
    \subsection{\subtwoone}
      \begin{frame}[t]{\subtwoone}
        \begin{example}
          \begin{enumerate}
            \item The dog likes to eat filet mignon.
            \item *Filet to dog eat mignon the likes.
          \end{enumerate}
        \end{example}
        \only<1-2>{
          \begin{block}{What's wrong with (2)?}
            \uncover<2->{
            The linguistic expressions are not combined in accordance with their syntactic properties
            }
          \end{block}
        }
        \only<3>{
          \begin{alertblock}{Linguistic expression}
            \input{\defs/part3/def_linguistic_expression.tex}
          \end{alertblock}
        }
        \only<4>{
          \begin{block}{Two types of linguistic expressions}
            \begin{itemize}
              \item \alert{Lexical expression}: \input{\defs/part3/def_lexical_expression.tex}
              \item \alert{Phrasal expression}: \input{\defs/part3/def_phrasal_expression.tex}
            \end{itemize}
          \end{block}
        }
        \only<5-6>{
          \begin{alertblock}{A grammatical sentence}
            \input{\defs/part3/def_grammatical_sentence.tex}
          \end{alertblock}
          \begin{alertblock}<6->{Grammaticality judgment}
            \input{\defs/part3/def_grammaticality_judgment.tex}
          \end{alertblock}
        }
      \end{frame}

    \subsection{\subtwotwo}
      \begin{frame}[t]{\subtwotwo}
        \begin{block}{}
          Some links exist between syntax and meaning, but grammaticality is unrelated to meaning
        \end{block}
        \only<2-3>{
          \begin{example}
            \begin{enumerate}
              \item The dog likes cats.
              \item Cats like the dog.
            \end{enumerate}
          \end{example}
          \only<2>{
            \begin{block}{Syntax can affect meaning}
              Flipping the subject and object yields a different meaning
            \end{block}
          }
          \only<3>{
            \begin{alertblock}<2->{Principle of compositionality (Frege, late 19th century)}
              \input{\defs/part3/def_principle_of_compositionality.tex}
            \end{alertblock}
          }
        }
        \only<4>{
          \begin{example}
            \begin{enumerate}
              \item Colorless green ideas sleep furiously.
              \item *Green sleep colorless furiously ideas. \parencite{chomsky_syntactic_2002}
            \end{enumerate}
          \end{example}
          \begin{block}{Grammaticality can be independent of meaning}
            \begin{itemize}
              \item (1) is nonsense but grammatical
              \item (2) is nonsense and ungrammatical
            \end{itemize}
          \end{block}
        }
        \only<5-6>{
          \begin{example}
            From a language learner:
            \begin{enumerate}
              \item (*)Me bought dog.
            \end{enumerate}
          \end{example}
          \begin{block}{}
            Understandable but not grammatical \emph{in your language}
          \end{block}
          \only<6>{
            \begin{alertblock}{However}
              This is grammatical \emph{in the learner's language}
            \end{alertblock}
          }
        }
        \only<7>{
          \begin{example}
            \begin{enumerate}
              \item The dog ate a filet mignon.
              \item The dog devoured a filet mignon.
              \item The dog ate.
              \item *The dog devoured.
            \end{enumerate}
          \end{example}
          \begin{block}{}
            Lexical meaning doesn't predict syntactic properties
          \end{block}
        }
      \end{frame}

    \subsection{\subtwothree}
      \begin{frame}{\subtwothree}
        \begin{block}{Try these}
          \textcite{dawson_language_2016}, chapter 5 exercise 3
        \end{block}
      \end{frame}

      \begin{frame}{References}
        \printbibliography
      \end{frame}
\end{document}
